---
title: "ETC3555 2018 - Lab 3"
author: "Cameron Roach"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

## Preliminaries

In this lab we will build our own SVM classifier from scratch.

```{r eval=FALSE}
install.packages("e1701")
```

## Exercises

### Exercise 1

Build a SVM classifier from scratch in R.

### Exercise 2

Compare your model to the `svm` function from the `e1701` package. Any differences in results? Why?

### Exercise 3

Add a radial basis transformation to your classifier. Compare results again.

### Exercise 4

Convert to a regression model. SVR.

### Exercise 5

Compare your SVR model to your baseline model on electricity data from first lab.

### Exercise 6

Having built your own SVM and SVR functions, what advantages can you see in building a machine learning algorithm from scratch? When would this approach be useful? When should you rely on existing functionality?
