---
title: "ETC3555 2018 - Lab 1"
author: "Cameron Roach"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

## Preliminaries

This lab will focus on working with data. We will cover

* Loading data into `R`
* Reshaping data frames
* Creating new variables
* Fitting models to multiple data sets.

This lab has been designed to reflect a real world scenario a data scientit may encounter. You will be required to create models that predict electricity demand for 1000 buildings using (simulated) smart meter data.

Before proceeding, ensure you have the latest version of `R` and RStudio installed on your computer. Install the required packages by running

```{r eval=FALSE}
install.packages(c("tidyverse", "randomForest"))
```

By the end of this lab you should be familiar with the tidyverse family of package and the purpose of each. You will also have a better understanding of how to produce a lot of work with a minimal amount of code.

## Exercises

### Exercise 1

Download the raw data files from __TODO__ and write a function to read them into `R`. Reshape the data into a tidy format. If you are unfamiliar with tidy datasets, please refer to Hadley Wickham's paper on the subject (available [here](https://www.jstatsoft.org/article/view/v059i10/v59i10.pdf)).

Once you have a tidy dataset convert the DT column data type from character type to datetime type using the `lubridate` package.

### Exercise 2

Adjust the below code to visualise monthly electricity demand for several of the buildings. Explain what each line of code does. What does the pipe operator, `%>%` do? How does this differ to the `+` method?

_Note: Plotting with the `ggplot2` package will be explored in detail in Lab 2._

```{r eval = FALSE}
elec_df %>% 
  filter(BID %in% sample(BID, 9)) %>%  
  gather(variable, value, kwh, temperature) %>% 
  ggplot(elec_df, aes(x = dt, y = kwh, colour = variable)) +
  geom_line() +
  facet_wrap(~BID, scales = "free_y") +
  labs(title = "Temperature and electricity demand.",
       x = "kWh",
       y = "Date")
```

### Exercise 3

We have now seen some simple examples that uses `dplyr` and `tidyr` functions. The `dplyr` package is used for filtering, summarising and mutating data. The `tidyr` package is used to reshape data frames. Use `dplyr`'s `mutate` function to add hour of day and season variables to your data frame. Should these new variables be nominal, ordinal or numeric? Can you think of any other predictors that may be useful?

### Exercise 4

Use `purrr`'s `nest` and `map` functions to fit separate random forest models to each building and store each model in a new column of the data frame. _Hint: this should only take a few lines of code._

### Exercise 5

Cross validation using `modelr`.

### Exercise 6

Extract CV RMSE scores and add to new column.